gilmore-nysds-2016

### 2016-08-16 nysds-2016/gilmore-nysds-2016.Rmd
final draft
final pre-talk

<div class="notes>
- Even when researcher try to replicate results with help from the original investigators, the results can fall short?
- Why? Methods sections can't possibly report all essential details due to time and space constraints.
</div>

## Adolph study

@@

@@

<div class="notes">
- It's all well and good to put data into a repository, but how do we get it out?
- It's been clear for some time that searching and filtering have revolutionized the way we access knowledge in almost every domain.
- I suggest that the same will be true in data science.
- At the moment, Databrary offers the ability to search for datasets based on participant or file characteristics.
- But, this search capability will surely grow, and so in the very near future, a researcher will be able to search for individual sessions or even segments of time when a particular event is occurring.
</div>

<iframe width="560" height="315" src="https://www.youtube.com/embed/ZAmZucyzyZM" frameborder="0" allowfullscreen></iframe>

@@

- Multiple levels of spatial, temporal resolution
- Linked data sets and streams
- Key linkage variables: *when* (time), *where* (location), *who* (age, gender)
- Video is a spatially and temporally rich time series

@@

<iframe src="https://github.com/databrary/presentations/tree/master/nysds-2016" width=640px height=400px>
</iframe>

>>>>

@@

## What is the input to the developing brain?

<div class="centered">
<video width="700" height="550" controls>
  <source src="https://nyu.databrary.org/slot/11680/0,24500/asset/41871/download?inline=true" type="video/mp4">
Your browser does not support the video tag.
</video>

<div class="centered">
<video width="700" height="550" controls>
  <source src="https://nyu.databrary.org/slot/11680/25500,50000/asset/41873/download?inline=true" type="video/mp4">
Your browser does not support the video tag.
</video>

<div class="centered">
<video width="700" height="550" controls>
  <source src="https://nyu.databrary.org/slot/11680/51000,75500/asset/41875/download?inline=true" type="video/mp4">
Your browser does not support the video tag.
</video>

<iframe src="http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=7345450" width=640px height=400px>
</iframe>

@@

<div class="notes">
- It's all well and good to put data into a repository, but how do we get it out?
- It's been clear for some time that searching and filtering have revolutionized the way we access knowledge in almost every domain.
- I suggest that the same will be true in data science.
- At the moment, Databrary offers the ability to search for datasets based on participant or file characteristics.
- But, this search capability will surely grow, and so in the very near future, a researcher will be able to search for individual sessions or even segments of time when a particular event is occurring.
- The results of this search and filtering will be a custom dataset that can be reanalyzed and reused.
</div>

@@

- Multiple levels of spatial, temporal resolution
- Linked data sets and streams
- Key linkage variables: *when* (time), *where* (location), *who* (age, gender, race/ethnicity, ...)
- Video is a spatially and temporally rich time series

@@

<div class="centered">
<img src="img/github-screenshot.jpg" width=900px>

</div>
